% Created 2024-03-01 Fri 21:50
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Dan Schmidt}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Dan Schmidt},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.2 (Org mode 9.6.15)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\section{HEADER}
\label{sec:orgcaaced2}
:PROPERTIES:
:Name: Daniel Schmidt
:Address: Palatine, IL 60067
:Phone: 224.253.3388
:Email: daniel.adam.schmidt@gmail.com

\section{SKILLS}
\label{sec:org7be7b5d}
\begin{itemize}
\item Ability to work independently and problem solve in a fast-paced environment.
\item Effectively communicate with customers and teammates.
\item Strong technological aptitude.
\item Knowledge of Windows, Word, Excel, Linux, Bash.
\end{itemize}

\section{EXPERIENCE}
\label{sec:org7a0fddc}
\subsection{Berndt Snow Inc Palatine IL}
\label{sec:orgb1a581a}

\subsection{Amazon Locker+  Schaumburg IL}
\label{sec:orgbbe2de3}
Customer Associate Dec 12, 2022 - Present 

\subsection{True Blue Car Wash Palatine IL}
\label{sec:org591ff14}
Site Manager Apr 13, 2022 - Dec 12, 2022
\begin{itemize}
\item Ability to successfully recruit and onboard new employees, train and coach staff, schedule employee shifts, with strict adherence to overtime policies, perform activities around employee engagement, performance management, and recognition
\item Maintain a focus on growing sales volume and increasing site profitability
\item Manage operating P\&L metrics and understands how expenditures/costs impact business margins and pricing
\item Ensure that customers are satisfied and that any inquiries, incidents and issues are resolved in a timely manner
\item Ensure the site follows all approved safety procedures
\item Ensure the site follows all approved vehicle damage claim procedures
\item Performs other duties and responsibilities as assigned
\end{itemize}

\subsection{KC’s Car Wash Palatine IL}
\label{sec:org8aa2305}
Assistant Manager Aug 24, 2020 - Apr 13, 2022
\begin{itemize}
\item Safely directing customers' vehicles into the wash tunnel.
\item Monitoring vehicles and equipment during the wash process.
\item Serving customers in the sale of wash packages and gift cards.
\item Addressing customers' questions and concerns in a calm, friendly and professional manner.
\item Maintaining the cleanliness of the lot and operation of the vacuums.
\item Closing the facilities.
\end{itemize}


\section{EDUCATION}
\label{sec:orgb500ae3}
\subsection{CompTIA A+}
\label{sec:orga4070d3}

\subsection{College of Lake County 2011 - 2013}
\label{sec:org76d0de6}
Studied Linux System Administration and Networking
\end{document}
