\documentclass{simplecv}
\usepackage[a4paper, top=24pt]{geometry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}
\pagestyle{empty} % Remove page numbering
\title{Curriculum Vitea of Daniel Schmidt}
\author{Daniel Schmidt}
\date{\today}
\renewcommand{\topicmargin}{0.06\columnwidth}

\begin{document}

 \rightheader{264 W Jennifer Ln\\
Palatine, IL 60067}

\leftheader{TEL: 224-253-3388\\
\href{mailto:daniel.adam.schmidt@gmail.com}{\text{\small daniel.adam.schmidt@gmail.com}}}

\title{Daniel Schmidt}
\maketitle\
Proficient CompTIA A+ certificate holder with strong technical troubleshooting skills, adept problem-solving abilities, and a commitment to customer service excellence. Detail-oriented and adaptable, with efficient time management and collaborative teamwork capabilities. Trained in hardware and software support, with a focus on delivering timely solutions and maintaining client satisfaction.

\section{Work Experience}
\begin{topic}
\item[Plow Operator \& Property Maintenance Tech, Berndt Snow Inc. Nov 2007 -- Present]
Operated snow plow trucks, snow blowers, and salt spreaders during winter months, ensuring safe and efficient removal of snow and ice from roads and properties. Adapted to changing weather conditions and worked effectively under pressure to maintain clear pathways.

During summer months, executed property maintenance contracts, specializing in landscaping and painting services. Demonstrated attention to detail and craftsmanship while enhancing outdoor spaces and revitalizing property aesthetics. Flexibility to transition between seasonal responsibilities while maintaining high standards of workmanship and customer satisfaction.
\end{topic}

\begin{topic}
\item[Site Manager - TrueBlue Car Wash, Apr 2022 -- Dec 2022]
Managed all aspects of employee recruitment, onboarding, training, and scheduling while enforcing overtime policies and fostering employee engagement. Oversaw sales growth initiatives, profitability management, and financial metrics comprehension, ensuring business sustainability. Prioritized customer satisfaction through timely issue resolution and adherence to safety procedures and vehicle damage claim protocols. Maintained a focus on operational efficiency and site profitability while promoting a positive work environment. Demonstrated adaptability and flexibility in fulfilling additional duties as required.
\end{topic}

\begin{topic}
\item[Assistant Manager - KC's Car Wash, Jun 2020 -- Apr 2022]
As Assistant Manager at the car wash, responsibilities included safely directing vehicles into the wash tunnel and monitoring the wash process. Additionally, served customers by selling wash packages and addressing inquiries in a professional manner. Ensured cleanliness of the lot and proper operation of equipment, including vacuums. Concluded daily operations by closing facilities.
\end{topic}

\section{Education}

\begin{topic}
\item[CompTIA A+ Certification]
Date of Certification:  Oct 2023

\href{https://drive.google.com/file/d/1AEhKVefmBUfZywOPLIuJx9v0ueqqA3CI/view?usp=sharing}{Proof of Certification}

\end{topic}

\end{document}
